---
title: "Aides Drug"
author: "mariahlynn"
date: "7/25"
output: html_document
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
triUmp <-read.csv(file="triUmpsal.csv",header=TRUE)

druggies =select(triUmp, c(treatment, infected, DrugUser))
druggies = filter(druggies, DrugUser == "yes")

```


# Introduction


<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?.  If you skimp in this section expect to be marked down in your grade. Paint a picture of the project a couple of paragraphs is expected!-->
A new  preventative aides drug (triUmpsal) is under test in clinical trials. Consider only the DrugUsers, does this drug seem effective?  Hint - use dplyr to obtain that subpopulation with the filter command.

$H_0$: triUmpsal has no effect on preventing AIDS among DrugUsers.    
$H_A$: triUmpsal is effective in preventing AIDS among DrugUsers.     

# Methods



<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method. Discuss what data manipulations may be needed for example subsetting or other binning procedures and what sort of graphical displays and inferential tools will be used!-->

treatment is a xxxx variable  
infected is a xxxxxxxxx variable,  
so I use the xxx~yyy helper file   

# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->


## Descriptive Results

### Graphical Descriptive Results

```{r}
barchartGC(~infected + treatment,data=druggies)
barchartGC(~infected + treatment,data=druggies, type="percent")

```
The barchart above shows the distribution of infection outcomes(infected or not infected) among DrugUsers based on whether they received triUmpsal or not. The first chart shows raw counts. While the seocnd chart displays percentages. These graphical representations aloow us to visually assess any differences in infection rates bwteen the treatment and control groups. 

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question. Bottom line is to explain the features of the graph that are relevant to conforming or departing to what is expected by your null hypothesis !-->

### Numerical Descriptive Results

```{r}
table1<- xtabs(~infected + treatment, data=druggies) 
rowPerc(table1)
colPerc(table1)
```
Those with the drug has a less change of being affected. 

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```
The P-value is 0.0000001242, therefore less than 0.05. TriUmpsal has a positive affect on the prevention of AIDS. 

The fisher test has a 95% confidence interval. 

# Discussion and Conclusion
Based on the graphical and numerical analyses conducted, we discussed the implications of our findings that regard the effectiveness of triUmpsal in preventing AIDS among DrugUsers. If a relationship was found we considered whether th treatment might be casually linked to the reduced infection rates or if other factors could explain the observed association.
In conclusion, this study provides valuable insights into potential effectiveness of triUmpsal as a preventative AIDS drug specifically among DrugUsers. Further research and potentially larger-scale trials may be warranted to validate these findings and explore additional factors influencing treatment outcomes.

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
